### 2023-11-28 paper/draft.tex

What is the formula for $\alpha_i$? <TBD> \\

@@

%O(N^2) version with ascending sort
\begin{align}
    \frac{1}{n} \sum_{i=1}^{n-1} \frac{\sum_{j=i+1}^n\ell([f(x_{i:n})]_{1:k},y_j)}{(n-i)}\label{eq:aurcloss_n2}
\end{align}

$\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$ in descending order.

%O(N) version with descending sort and assumes zero-based numbering
\begin{align}
    \frac{1}{n} \sum_{i=1}^{n} \frac{1}{i} \sum_{j=0}^{i-1}\ell([f(x_{\pi_j})]_{1:k},y_{\pi_j})
    \label{eq:aurcloss_n}
\end{align}

@@

\begin{itemize}
    \item $\mathcal{O}(n)$ algorithm implemented and converted to differentiable loss function $\ell_{\mathrm{AURC}}$
    \item batch approximation to test consistency
    \item training with $\ell_{\mathrm{AURC}}$ and test effect of different batch sizes
    \item Literature review on differentiable \AURC TBD
    \begin{enumerate}
        \item \cite{cao2022generalizing} close in spirit, dependent on cost, similarly defines it as a $K+1$ classification problem. 
    \end{enumerate}
\end{itemize}

>>>>

What is the formula for $\alpha_i$?  \\

Matthew's guess (sorted ascending)
\begin{align}
\alpha_i = \frac{1}{n} \sum_{j=1}^{i-1} \frac{1}{n-j}
\end{align}
The $n$th harmonic number is given by
\begin{align}
    H_n := \sum_{k=1}^n \frac{1}{k} = \psi(n+1) + \gamma
\end{align}
where $\gamma \approx 0.577$ is the Euler–Mascheroni constant and $\psi(n) := \frac{\Gamma'(n)}{\Gamma(n)}$ is the digamma function.\footnote{\url{https://mathworld.wolfram.com/HarmonicSeries.html}}
Written in terms of harmonic numbers
\begin{align}
    \alpha_i = \frac{1}{n} \left( H_{n-1} - H_{n-i} \right) = \frac{1}{n} \left( \psi(n) - \psi(n-i+1) \right).
\end{align}
Setting $i=\beta n$ for some $0<\beta<1$ and taking the limit
\iffalse
\begin{align}
    \lim_{n\rightarrow \infty} H_{n-1} - H_{n - \beta n} \approx& \lim_{n\rightarrow \infty} \ln (n-1) - \ln (1-\beta)n \\
    =& \lim_{n\rightarrow \infty} \ln (n-1) - \ln n - \ln (1-\beta) =  -\ln (1-\beta) \implies \\
    \alpha_i \approx& -\ln \left(1 - \frac{i}{n}\right)
\end{align}
\todo[inline]{Double check what we get if we derive the limit using the digamma function  in place of the logarithm.  The below derivation is technically more principled than above.}
\fi
\begin{align}
    \lim_{n\rightarrow \infty} H_{n-1} - H_{n-\beta n} =& \lim_{n\rightarrow \infty} \psi(n) - \psi(n-\beta n+1) = \lim_{n\rightarrow \infty} \psi(n) - \psi((1-\beta) n) - \frac{1}{(1-\beta) n} \\
    =& \lim_{n\rightarrow \infty} \ln(n) - \frac{1}{2n} - \ln((1-\beta) n) + \frac{1}{2(1-\beta)n} - \frac{1}{(1-\beta)n} \label{eq:digammaAsymptoticLnPlus} \\
    =& \lim_{n\rightarrow \infty}   - \frac{1}{2(1-\beta)n}  - \frac{1}{2n}  -\ln (1-\beta) \\
    =& -\ln (1-\beta) \implies \\
    \alpha_i \approx& -\ln \left(1 - \frac{i}{n}\right)
\end{align}
where Equation~\eqref{eq:digammaAsymptoticLnPlus} was obtained using the asymptotic result that $\psi(n) \rightarrow \ln n - \frac{1}{2n}$ as $n \rightarrow \infty$.

This looks closely related to Equation (3) of  \url{https://arxiv.org/pdf/1805.08206.pdf }

@@

Teodora's guess:
%O(N^2) version with ascending sort
\begin{align}
    \operatorname{AURC}(f) = \frac{1}{n} \sum_{i=1}^{n-1} \frac{\sum_{j=i+1}^n\ell([f(x_{j})]_{1:k},y_j)}{(n-i)}\label{eq:aurcloss_n2}
\end{align}

% with $\alpha_i = \sum_{j=i+1}^n 1 $

$\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{0\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{0\leq i \leq n}$ in descending order.

%O(N) version with descending sort and assumes zero-based numbering
\begin{align}
    \frac{1}{n} \sum_{i=1}^{n} \frac{1}{i} \sum_{j=1}^{i-1}\ell([f(x_{\pi_j})]_{1:k},y_{\pi_j})
    \label{eq:aurcloss_n}
\end{align}

@@

\begin{itemize}
    \item $\mathcal{O}(n)$ algorithm implemented and converted to differentiable loss function $\ell_{\mathrm{AURC}}$
    \item batch approximation to test consistency
    \item training with $\ell_{\mathrm{AURC}}$ and test effect of different batch sizes
    \item Literature review on differentiable \AURC{} TBD
    \begin{enumerate}
        \item \cite{cao2022generalizing} close in spirit, dependent on cost, similarly defines it as a $K+1$ classification problem. 
    \end{enumerate}
\end{itemize}
